Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-22 pkg/disttree/inst/draft/draft.Rnw
added computational details for supplements and corrected a few typos
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2354 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 782ebafa479aad5324d6874ee64c2dff4006a85a

\subsubsection{Distributional specifications}
%% choice of distribution mit Verweis auf Supplement distributions
\hlc{Choosing an adequate distributional family is a crucial step and forms
the basis required to build a well fitting model. Therefore, this
decision should be made thoughtfully. 
In the presented application we applied a Gaussian distribution left-censored 
at zero as this has proven to be a well working choice in
earlier literature} \citep{Stauffer+Mayr+Messner:2017}. 
\hlc{To test for robustness against distributional misspecifation 
different distributional assumptions have been considered as well. 
In Supplement 1 (Different Response Distributions) the exact
same evaluations as in} Section~\ref{sec:all} \hlc{are carried out for 15
observation stations, once employing a Gaussian hurdle model and once
with a logistic distribution left-censored at zero in order to account
for heavier tails. Under both assumptions the obtained results 
are similar to those presented in the paper applying a Gaussian distribution
left-censored at zero. In some settings the hurdle model leads to slight 
improvements, but this comes with more variability (especially for EMOS and the 
boosted GAMLSS). For the boosted GAMLSS the left-censored logistic distribution
shows slightly better results, however, only within a range of less than $2\%$
and not for all stations. Altogether, the distributional forest has proven to be 
very robust against distributional misspecifications.

Alternatively, a distribution including an additional parameter capturing skewness}
\citep{Scheuerer+Hamill:2015, Baran+Nemoda:2016} \hlc{could be applied. For example, 
in transformation forests} \citep{Hothorn+Zeileis:2017} \hlc{a very flexible 
five-parametric distribution family is employed such that skewness can be modeled 
explicitly.
Evaluating further distributions might be of interest but this would go beyond the
scope of this manuscript.
}

@@

The fitted distributional forest for July 24 and
observation station Axams (including Figure~\ref{fig:axams-dist})
is reproducible using 
\code{demo("RainAxams", package = "disttree")}.
This also includes fitting the other zero-censored
Gaussian models considered in this paper and generating the corresponding 
QQ~plots (Figure~\ref{fig:axams-qq}) and PIT histograms 
(Supplement 2: Stationwise Evaluation).
Full replication of all results can be obtained with
\code{demo("RainTyrol", package = "disttree")}
requiring the companion \textsf{R} package \textbf{RainTyrol} (version~\Sexpr{packageVersion("RainTyrol")}),
also available within the \textsf{R}-Forge~project.

>>>>

\subsubsection{Distributional specifications}
%% choice of distribution mit Verweis auf Supplement distributions
\hlc{Choosing an adequate distributional family is a crucial step and forms
the basis required to build a well fitting model. Therefore, this
decision should be made thoughtfully. 
In the presented application we applied a Gaussian distribution left-censored 
at zero as this has proven to be a well working choice in
earlier literature} \citep{Stauffer+Mayr+Messner:2017}. 
\hlc{To test for robustness against distributional misspecifation 
different distributional assumptions have been considered as well. 
In Supplement 1 (Different Response Distributions) the exact
same evaluations as in} Section~\ref{sec:all} \hlc{are carried out for 15
observation stations, once employing a Gaussian hurdle model and once
with a logistic distribution left-censored at zero in order to account
for heavier tails. Under both assumptions the obtained results 
are similar to those presented in the paper applying a Gaussian distribution
left-censored at zero. In some settings the hurdle model leads to slight 
improvements, but this comes with more variability (especially for EMOS and the 
boosted GAMLSS). For the boosted GAMLSS the left-censored logistic distribution
shows slightly better results, however, only within a range of less than $2\%$
and not for all stations. Altogether, the distributional forest has proven to be 
very robust against distributional misspecifications.}

\hlc{Alternatively, a distribution including an additional parameter capturing 
skewness could be applied} \citep{Scheuerer+Hamill:2015, Baran+Nemoda:2016}. 
\hlc{For example, in transformation forests} \citep{Hothorn+Zeileis:2017} 
\hlc{a very flexible five-parametric distribution family is employed such 
that skewness can be modeled explicitly.
Evaluating further distributions might be of interest but this would go beyond the
scope of this manuscript.
}

@@

The fitted distributional forest for July 24 and
observation station Axams (including Figure~\ref{fig:axams-dist})
is reproducible using 
\code{demo("RainAxams", package = "disttree")}.
This also includes fitting the other zero-censored
Gaussian models considered in this paper and generating the corresponding 
QQ~plots (Figure~\ref{fig:axams-qq}) and PIT histograms 
(Supplement 2: Stationwise Evaluation).
Full replication of all results can be obtained with
\code{demo("RainTyrol", package = "disttree")}
requiring the companion \textsf{R} package \textbf{RainTyrol} (version~\Sexpr{packageVersion("RainTyrol")}),
also available within the \textsf{R}-Forge~project.
The results presented in Supplement 1 (Different Response Distributions) and 
Supplement 2 (Stationwise Evaluation) can be reproduced using
\code{demo("RainDistributions", package = "disttree")} and 
\code{demo("RainStationwise", package = "disttree")} respectively.

### 2018-10-22 pkg/disttree/inst/draft/rejoinder.Rnw
further revisions based on reviews
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2348 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: f085d88cc0b20e11401fa7b30d38ad5601ed0a2f
added computational details for supplements and corrected a few typos
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2354 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 782ebafa479aad5324d6874ee64c2dff4006a85a

As stopping criteria the minimal number of observations to perform 
a split (\texttt{minsplit}) is set to 50, the minimal number of 
observations in a terminal node (\texttt{minbucket}) is set to 20 
and early stopping (or ``pre-pruning'') based on the significance level is disabled
(by setting \texttt{alpha} to 1). We have added this information in 
the manuscript in Section~3.2, `Distributional forest', and
also discussed the choice of these tuning parameter in Section~4 and
in the answer to the second point of the associate editor.

@@

As you correctly point out, another way to deal with skewness is to
use an extended distributional specification (e.g., Scheuerer and Hamill 2015,
Baran and Nemoda 2016). This increases the complexity of the statistical
models and makes the comparison to publications based on power transformations
more difficult. Therefore, we feel that this exceeds the scope of this
contribution but we do discuss it in Section~4 as being of interest for
future research. \fixme{Include one or two sentences about this as an
outlook in the discussion of distributional specifications.}

@@

In this sense, distributional forests are appealing for weather
forecasting tasks because the focus is not so much on interpretation
but often much more on: (a)~forecasting skill and (b)~(semi-)automatic
application of models on a larger domain. See also the discussion
in, e.g., Rasp and Lerch 2018).

We have adapted our manuscript to reflect that we focus on forecasting
skill in a large number of models -- and not so much on interpretation.

\fixme{Where should this be pointed out in the manuscript? 
Z: Both in the introduction when the ``zoo'' of regression techniques
is introduced -- and again in the discussion (possibly along with
variable selection?).}

@@

In order to investigate these questions we have carried out the full
analysis as presented for station Axams in the main manuscript for 14
further observation stations. It shows that the distributional
forest is very robust against distributional (mis)specifications
and almost always competitive with the best among the other methods 
or even better. The exact results are provided in 
Supplement 2 (Stationwise Evaluation) and discussed in Section~4. 
Especially for meteorologists intending to apply model output 
statistics (MOS) for dozens or hundreds of observation stations 
(e.g., Wahl 2014, Rasp and Lerch 2018)
the distributional forest provides a good and robust alternative. 
Computational costs are clearly higher than for a basic EMOS model, 
but similar to a prespecified GAMLSS and lower than for GAMLSS
using variable selection by cross-validation. Fitting and forecasting
times are reported now in Supplement~2 (Stationwise Evaluation).

Regarding forecasting tasks other than the one presented in
the manuscript, we would \emph{not} expect that distributional
forests are \emph{``generally better''}. As for (boosted) GAMs and
random forests we would expect that sometimes (boosted) GAMLSS and
sometimes distributional forests perform better. As already argued
above we see the methods as complements not substitutes.

\fixme{Refer again to the corresponding point in the manuscript.}

>>>>

As stopping criteria the minimal number of observations to perform 
a split (\texttt{minsplit}) is set to 50, the minimal number of 
observations in a terminal node (\texttt{minbucket}) is set to 20 
and early stopping (or ``pre-pruning'') based on the significance level is disabled
(by setting \texttt{alpha} to 1). We have added this information in 
the manuscript in Section~3.2, `Distributional forest', and
also discussed the choice of these tuning parameters in Section~4 and
in the answer to the second point of the associate editor.

@@

As you correctly point out, another way to deal with skewness is to
use an extended distributional specification (e.g., Scheuerer and Hamill 2015,
Baran and Nemoda 2016). This increases the complexity of the statistical
models and makes the comparison to publications based on power transformations
more difficult. Therefore, we feel that this exceeds the scope of this
contribution but we do discuss it in Section~4 as being of interest for
future research. 
%\fixme{Include one or two sentences about this as an
%outlook in the discussion of distributional specifications.}

@@

In this sense, distributional forests are appealing for weather
forecasting tasks because the focus is not so much on interpretation
but often much more on: (a)~forecasting skill and (b)~(semi-)automatic
application of models on a larger domain. See also the discussion
in, e.g., Rasp and Lerch (2018).

We have adapted our manuscript in Section~1 and Section~4, \textit{Variable Selection}, 
to reflect that we focus on forecasting skill in a large number of 
models -- and not so much on interpretation.

%\fixme{Where should this be pointed out in the manuscript? 
%Z: Both in the introduction when the ``zoo'' of regression techniques
%is introduced -- and again in the discussion (possibly along with
%variable selection?).}

@@

In order to investigate these questions we have carried out the full
analysis as presented for station Axams in the main manuscript for 14
further observation stations. It shows that the distributional
forest is %very robust against distributional (mis)specifications and (FIXME: this is shown in Supplement 1)
almost always competitive with the best among the other methods 
or even better. The exact results are provided in 
Supplement 2 (Stationwise Evaluation) and discussed in Section~4. 
Especially for meteorologists intending to apply model output 
statistics (MOS) for dozens or hundreds of observation stations 
(e.g., Wahl 2014, Rasp and Lerch 2018)
the distributional forest provides a good and robust alternative. 
Computational costs are clearly higher than for a basic EMOS model, 
but similar to a prespecified GAMLSS and lower than for GAMLSS
using variable selection by cross-validation. Fitting and forecasting
times are reported now in Supplement~2 (Stationwise Evaluation).

Regarding forecasting tasks other than the one presented in
the manuscript, we would \emph{not} expect that distributional
forests are \emph{``generally better''}. As for (boosted) GAMs and
random forests we would expect that sometimes (boosted) GAMLSS and
sometimes distributional forests perform better. As already argued
above we see the methods as complements not substitutes.
This is now also mentioned in Section~1 and discussed in Section~4,
\textit{Variable Selection}.

%\fixme{Refer again to the corresponding point in the manuscript.}
